manuscript - APP

### 2018-09-25 R/manuscript_app.Rmd
changes according the paper changes

```{r exp1b  - load data}
df_exp1b <- readRDS(file.path(data_pth,"exp1b","responses","responses_150622.rds")) %>% 
  filter(block != 0)

@@

df2_exp1b <- rbind(df_exp1b,df_exp1b)
df2_exp1b$version <- 2
df2_exp1b$version[1:nrow(df_exp1b)] <- 1

# this is a little hack, just to make a correct ggplot with one line
tmp <- df_exp1b$restk
df2_exp1b$restk[df2_exp1b$version == 2] <- df_exp1b$type
df2_exp1b$type[df2_exp1b$version == 2] <- tmp

df2_exp1b$version <- factor(df2_exp1b$version, labels = c("fix distractors' k", "fix target's k"))
```

@@

```{r Figure 3}

p_k2 <- plot_fig3(2)
p_k4 <- plot_fig3(4)
p_k8 <- plot_fig3(8)
p_k16 <- plot_fig3(16)
p_k64 <- plot_fig3(64)
p_k64_legend <- plot_fig3(64, show_legend = T)

gridExtra::grid.arrange(p_k2,p_k4, p_k8, p_k16, p_k64, ncol = 3)
ggsave(file.path(plot_pth, "Fig3_k2.eps"), p_k2, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig3_k4.eps"), p_k4, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig3_k8.eps"), p_k8, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig3_k16.eps"), p_k16, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig3_k64.eps"), p_k64, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig3_k64_legend.eps"), p_k64_legend, width = 6, height = 6)
# final plot was created in inkscape
```

@@

We run multiple within subject aova

@@

>>>>

```{r exp1b  - load data}
#df_exp1b <- readRDS(file.path(data_pth,"exp1b","responses","responses_150622.rds")) %>% 
  filter(block != 0)

@@

#df2_exp1b <- rbind(df_exp1b,df_exp1b)
#df2_exp1b$version <- 2
#df2_exp1b$version[1:nrow(df_exp1b)] <- 1

# this is a little hack, just to make a correct ggplot with one line
#tmp <- df_exp1b$restk
#df2_exp1b$restk[df2_exp1b$version == 2] <- df_exp1b$type
#df2_exp1b$type[df2_exp1b$version == 2] <- tmp

#df2_exp1b$version <- factor(df2_exp1b$version, labels = c("fix distractors' k", "fix target's k"))

df_exp1b <- 
  readRDS(
    file.path(data_pth, "exp1b", "responses", "responses_150622.rds")) %>% 
  filter(block != 0) %>% as_tibble(.) %>% 
  rename(targetk = type) %>% mutate(id = factor(subject)) %>% 
  mutate(contrast_abs = abs(log2(targetk / restk)), 
         target_straight = (targetk > restk),
         ratio = (besselI(restk,0) * exp(targetk)) / (besselI(targetk,0) * exp(restk)),
         ratio_abs = abs(log((besselI(restk,0) * exp(targetk))) / (besselI(targetk,0) * exp(restk))),
         ratio_abs = abs(log(
           (besselI(restk,0) * exp(targetk))) / (besselI(targetk,0) * exp(restk))))
```

@@

```{r Figure 3}
accu_summary <- df_exp1b %>% 
  mutate(contrast_abs_f = as.character(contrast_abs)) %>% 
  group_by(id, contrast_abs, contrast_abs_f, target_straight) %>% 
  dplyr::summarise(accu = mean(accuracy), n = n()) %>% 
  ungroup()
accu_summary_wo_0 <- accu_summary %>% filter(contrast_abs > 0)

# duplicated values for contrast 0
accu_summaryx <- bind_rows(
  accu_summary,
  accu_summary %>% 
    filter(contrast_abs == 0, target_straight == F) %>% 
    mutate(target_straight = T)
)

p <- accu_summaryx %>% 
  ggplot(
    aes(x = contrast_abs, y = accu, 
        group = target_straight, shape = target_straight, linetype = target_straight)) + 
  stat_summary(fun.data = "mean_cl_boot", alpha = .5) +
  stat_summary(fun.y = "mean", alpha = .5, geom = "line") + 
  theme(aspect.ratio = 1) + 
  scale_shape_discrete("Distractor type", labels = c("More Ballistic-like", "More Brownian-like")) +
  scale_linetype_discrete("Distractor type", labels = c("More Ballistic-like", "More Brownian-like")) +
  xlab("contrast") + ylab("Accuracy")
ggsave(file.path(plot_pth, "Figure3.png"), p, width = 9, height = 6)
```

@@

We run multiple within subject anova

@@

# Appendix

```{r}
#p_k2 <- plot_fig3(2)
#p_k4 <- plot_fig3(4)
#p_k8 <- plot_fig3(8)
#p_k16 <- plot_fig3(16)
#p_k64 <- plot_fig3(64)
#p_k64_legend <- plot_fig3(64, show_legend = T)

#gridExtra::grid.arrange(p_k2,p_k4, p_k8, p_k16, p_k64, ncol = 3)
#ggsave(file.path(plot_pth, "Fig3_k2.eps"), p_k2, width = 6, height = 6)
#ggsave(file.path(plot_pth, "Fig3_k4.eps"), p_k4, width = 6, height = 6)
#ggsave(file.path(plot_pth, "Fig3_k8.eps"), p_k8, width = 6, height = 6)
#ggsave(file.path(plot_pth, "Fig3_k16.eps"), p_k16, width = 6, height = 6)
#ggsave(file.path(plot_pth, "Fig3_k64.eps"), p_k64, width = 6, height = 6)
#ggsave(file.path(plot_pth, "Fig3_k64_legend.eps"), p_k64_legend, width = 6, height = 6)
# final plot was created in inkscape
```

### 2018-09-25 R/manuscript_app_alt_clean.Rmd
change axis description
changes according the paper changes

```{r Charts1b}
#accu_summary %>% 
#  ggplot(aes(x = contrast_abs, y = accu, colour = target_straight)) + 
#  geom_jitter() 
accu_summaryx %>% 
  ggplot(
    aes(x = contrast_abs, y = accu, 
        group = target_straight, shape = target_straight, linetype = target_straight)) + 
  stat_summary(fun.data = "mean_cl_boot", alpha = .5) +
  stat_summary(fun.y = "mean", alpha = .5, geom = "line") +

  theme(aspect.ratio = 1) + 
  xlab("c") + ylab("Accuracy")
```

@@

  theme(aspect.ratio = 1) + 
  xlab("kl distance") + ylab("Accuracy") +scale_x_log10()
```

>>>>

```{r Charts1b}
#accu_summary %>% 
#  ggplot(aes(x = contrast_abs, y = accu, colour = target_straight)) + 
#  geom_jitter() 
accu_summaryx %>% 
  ggplot(
    aes(x = contrast_abs, y = accu, 
        group = target_straight, shape = target_straight, linetype = target_straight)) + 
  stat_summary(fun.data = "mean_cl_boot", alpha = .5) +
  stat_summary(fun.y = "mean", alpha = .5, geom = "line") + 
  theme(aspect.ratio = 1) + 
  scale_shape_discrete("Target straighter") + 
  xlab("contrast") + ylab("Accuracy")
```

@@

  theme(aspect.ratio = 1) + 
  xlab("PDF ratio") + ylab("Accuracy") +scale_x_log10()
```
